---
title: "ERNA_SHP"
author: "Jonathan Amegin"
date: "2024-09-05"
output: html_document
---
```{r}
library(tidyverse)
library(dplyr)
library(sf)
library(shapefiles)
library(readr)
library(ggplot2)
library(lubridate)

setwd("~/R documents/ERNA_survey_SHP")

plant_1 <- read_csv("data/plant_1.csv")
row_blocks <- read_csv("data/_2024_ERNA_GrasslandRestoration_BLM_ChatfieldCommonGarden_0.csv")
```
Need to make a spatial plot design with 40 rows, subsets of 4 rows/block (10 blocks). Each row has 20-30 plants. 
Individual plants have the Block/row combos already in data. 
Maybe a 'case_when' mutation to create a coordinate system? e.i each block number represents a meter mark, and the plant position equals a multiple of 15cm along the row?
```{r}
erna <- left_join(plant_1, row_blocks[,c(2,7,8)], join_by("ParentGlobalID" == "GlobalID"), relationship = "many-to-one")

erna_design <- erna  %>% 
mutate( x_coord = (`Block` - 1) + (`Row In Block` * 0.25)) 

erna_design$date = substr(erna_design$date, 1, nchar(erna_design$date)-2)
erna_design$date = mdy_hms(erna_design$date)
 
erna_points <- erna_design[, c("plantID_db", "ObjectID", "Plant Position In Row", "x_coord")]



erna_design %>% 
  group_by(Block, `Row In Block`, date) %>% 
  summarise( n_surv = sum(survival)) %>% 
  ggplot(mapping = aes( x = date, y = n_surv)) +
  geom_col()
```

Need to make a spatial plot design with 40 rows, subsets of 4 rows/block (10 blocks). Each row has 20-30 plants. 
Individual plants have the Block/row combos already in data. 
Maybe a 'case_when' mutation to create a coordinate system? e.i each block number represents a meter mark, and the plant position equals a multiple of 15cm along the row?


Realized the Survey123 data has errors due to corrections made on back end. Need to use the data updates and bind them together. 

```{r}
## correct_data <- paste("data/corrected_data/" , list.files(path = "data/corrected_data", pattern = "\\.csv$"), sep = "" ) %>% 
##    map_df(~read_csv(.))

n_distinct(correct_data$plantID)

correct_data$date = mdy(correct_data$date)


correct_data <- lapply(paste("data/corrected_data/" , list.files(path = "data/corrected_data", pattern = "\\.csv$"), sep = "" ), read_csv)

erna2 <- correct_data %>% reduce(full_join, by = "date")

erna1[is.na(erna1)] <- 0



```

